---
title: "Final Project - Delaney Smith"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
## Introduction
  This is where I describe the project

## Methods
**1) Load in Libraries and Data**
    This step is necessary to ensure that we have the necessary packages installed to be able to run specific functions.
```{r Library, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(modelr)
library(moderndive)
library(gapminder)
library(broom)
library(knitr)
library(stargazer)
```
**2) Load in Data and Change Titles**
  In this section I loaded in my original data set. Then I had to change the column titles to match the original dataset.
```{r Load Data, include=FALSE}
marissa_data1 <- read.csv('~/R/Final_Project/Final_Project_Data.csv', header=T, na.strings=".")
#Change column headers
marissa_data <- marissa_data1 %>% 
  rename(
    Sex = M.F,
    LarvaeAge = Age.month,
    InVitroViability = In.Vitro.Viability,
    InVitroExsheathment = In.vitro.Exsheathment,
    InVivoViability = In.Vivo.Viability,
    InVivoExsheathment = In.Vivo.Exsheathment
    )
```

**3) Sort Data by Cycle and Sort Out NA Values**
  From that original data set I went through and created subgroups of data sets for each cycle we were interested. After that I created more data sets that filtered out the specific rows that contained NA values for use in specific models.
```{r Sorting Data, include=FALSE}
cycle_1 <- filter(marissa_data, Cycle == 1)
cycle_2 <- filter(marissa_data, Cycle == 2)
cycle_3 <- filter(marissa_data, Cycle == 3)
cycle_4 <- filter(marissa_data, Cycle == 4)
cycle_5 <- filter(marissa_data, Cycle == 5)
no_InVitro_comp_data <- filter(marissa_data, !is.na(InVitroViability))
cycle_1NA_vitro <- filter(cycle_1, !is.na(InVitroViability))
cycle_1NA_hatch <- filter(cycle_1, !is.na(Hatchability))
cycle_2NA_vitro <- filter(cycle_2, !is.na(InVitroViability))
cycle_2NA_hatch <- filter(cycle_2, !is.na(Hatchability))
cycle_3NA_vitro <- filter(cycle_3, !is.na(InVitroViability))
cycle_3NA_hatch <- filter(cycle_3, !is.na(Hatchability))
cycle_4NA_vitro <- filter(cycle_4, !is.na(InVitroViability))
cycle_4NA_hatch <- filter(cycle_4, !is.na(Hatchability))
cycle_5NA_vitro <- filter(cycle_5, !is.na(InVitroViability))
cycle_5NA_hatch <- filter(cycle_5, !is.na(Hatchability))
```

**4) Create Cycle Specific Models**
  In this section I wanted to create any and all form of exploratory model to test the various ways that Larvae Age has an impact on each variable. 
```{r Cycle Models, include=FALSE}
model_A1 <- lm(LarvaeAge ~ InVitroViability, data = cycle_1NA_vitro)
summary(model_A1)
model_B1 <- lm(LarvaeAge ~ InVitroExsheathment, data = cycle_1NA_vitro)
summary(model_B1)
model_C1 <- lm(LarvaeAge ~ InVivoViability, data = cycle_1)
summary(model_C1)
model_D1 <- lm(LarvaeAge ~ InVivoExsheathment, data = cycle_1)
summary(model_D1)
model_E1 <- lm(LarvaeAge ~ Hatchability, data = cycle_1NA_hatch)
summary(model_E1)
model_F1 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment, data = cycle_1NA_vitro)
summary(model_F1)
model_G1 <- lm(LarvaeAge ~ InVivoViability + InVivoExsheathment, data = cycle_1)
summary(model_G1)
model_H1 <- lm(LarvaeAge ~ InVitroViability + InVivoViability, data = cycle_1NA_vitro)
summary(model_H1)
model_I1 <- lm(LarvaeAge ~ InVitroExsheathment + InVivoExsheathment, data = cycle_1NA_vitro)
summary(model_I1)
model_J1 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment + 
                 InVivoViability + InVivoExsheathment + Hatchability, data = cycle_1NA_hatch)
summary(model_J1)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#Cycle 2
model_A2 <- lm(LarvaeAge ~ InVitroViability, data = cycle_2NA_vitro)
summary(model_A2) 
model_B2 <- lm(LarvaeAge ~ InVitroExsheathment, data = cycle_2NA_vitro)
summary(model_B2)
model_C2 <- lm(LarvaeAge ~ InVivoViability, data = cycle_2)
summary(model_C2)
model_D2 <- lm(LarvaeAge ~ InVivoExsheathment, data = cycle_2)
summary(model_D2)
model_E2 <- lm(LarvaeAge ~ Hatchability, data = cycle_2NA_hatch)
summary(model_E2)
model_F2 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment, data = cycle_2NA_vitro)
summary(model_F2)
model_G2 <- lm(LarvaeAge ~ InVivoViability + InVivoExsheathment, data = cycle_2)
summary(model_G2)
model_H2 <- lm(LarvaeAge ~ InVitroViability + InVivoViability, data = cycle_2NA_vitro)
summary(model_H2)
model_I2 <- lm(LarvaeAge ~ InVitroExsheathment + InVivoExsheathment, data = cycle_2NA_vitro)
summary(model_I2)
model_J2 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment + 
                InVivoViability + InVivoExsheathment + Hatchability, data = cycle_2NA_hatch)
summary(model_J2)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#Cycle 3
model_A3 <- lm(LarvaeAge ~ InVitroViability, data = cycle_3NA_vitro)
summary(model_A3) 
model_B3 <- lm(LarvaeAge ~ InVitroExsheathment, data = cycle_3NA_vitro)
summary(model_B3)
model_C3 <- lm(LarvaeAge ~ InVivoViability, data = cycle_3)
summary(model_C3)
model_D3 <- lm(LarvaeAge ~ InVivoExsheathment, data = cycle_3)
summary(model_D3)
model_E3 <- lm(LarvaeAge ~ Hatchability, data = cycle_3NA_hatch)
summary(model_E3)
model_F3 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment, data = cycle_3NA_vitro)
summary(model_F3)
model_G3 <- lm(LarvaeAge ~ InVivoViability + InVivoExsheathment, data = cycle_3)
summary(model_G3)
model_H3 <- lm(LarvaeAge ~ InVitroViability + InVivoViability, data = cycle_3NA_vitro)
summary(model_H3)
model_I3 <- lm(LarvaeAge ~ InVitroExsheathment + InVivoExsheathment, data = cycle_3NA_vitro)
summary(model_I3)
model_J3 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment + 
                 InVivoViability + InVivoExsheathment + Hatchability, data = cycle_3NA_hatch)
summary(model_J3)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#Cycle 4
model_A4 <- lm(LarvaeAge ~ InVitroViability, data = cycle_4NA_vitro)
summary(model_A4) 
model_B4 <- lm(LarvaeAge ~ InVitroExsheathment, data = cycle_4NA_vitro)
summary(model_B4)
model_C4 <- lm(LarvaeAge ~ InVivoViability, data = cycle_4)
summary(model_C4)
model_D4 <- lm(LarvaeAge ~ InVivoExsheathment, data = cycle_4)
summary(model_D4)
model_E4 <- lm(LarvaeAge ~ Hatchability, data = cycle_4NA_hatch)
summary(model_E4)
model_F4 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment, data = cycle_4NA_vitro)
summary(model_F4)
model_G4 <- lm(LarvaeAge ~ InVivoViability + InVivoExsheathment, data = cycle_4)
summary(model_G4)
model_H4 <- lm(LarvaeAge ~ InVitroViability + InVivoViability, data = cycle_4NA_vitro)
summary(model_H4)
model_I4 <- lm(LarvaeAge ~ InVitroExsheathment + InVivoExsheathment, data = cycle_4NA_vitro)
summary(model_I4)
model_J4 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment + 
                 InVivoViability + InVivoExsheathment + Hatchability, data = cycle_4NA_hatch)
summary(model_J4)
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#Cycle 5
model_A5 <- lm(LarvaeAge ~ InVitroViability, data = cycle_5NA_vitro)
summary(model_A5) 
model_B5 <- lm(LarvaeAge ~ InVitroExsheathment, data = cycle_5NA_vitro)
summary(model_B5)
model_C5 <- lm(LarvaeAge ~ InVivoViability, data = cycle_5)
summary(model_C5)
model_D5 <- lm(LarvaeAge ~ InVivoExsheathment, data = cycle_5)
summary(model_D5)
model_E5 <- lm(LarvaeAge ~ Hatchability, data = cycle_5NA_hatch)
summary(model_E5)
model_F5 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment, data = cycle_5NA_vitro)
summary(model_F5)
model_G5 <- lm(LarvaeAge ~ InVivoViability + InVivoExsheathment, data = cycle_5)
summary(model_G5)
model_H5 <- lm(LarvaeAge ~ InVitroViability + InVivoViability, data = cycle_5NA_vitro)
summary(model_H5)
model_I5 <- lm(LarvaeAge ~ InVitroExsheathment + InVivoExsheathment, data = cycle_5NA_vitro)
summary(model_I5)
model_J5 <- lm(LarvaeAge ~ InVitroViability + InVitroExsheathment + 
                 InVivoViability + InVivoExsheathment + Hatchability, data = cycle_5NA_hatch)
summary(model_J5)
```


**Cycle 1 Modeling Statistics**
```{r Cycle 1 Table, results='asis', message=FALSE, echo=FALSE, cache=TRUE}
stargazer(model_A1, model_B1, model_C1, model_D1, model_E1, model_F1, model_G1, model_H1, model_I1, model_J1, type = "html", notes.append = FALSE, notes.label = "Symbols", notes = c("<sup>&#42;</sup>p<0.1; <sup>&#42;&#42;</sup>p<0.05; <sup>&#42;&#42;&#42;</sup>p<0.01"), keep.stat = "adj.rsq", column.labels = c("A1", "B1","C1", "D1","E1", "F1","G1", "H1","I1", "J1"), multicolumn = TRUE, ci = TRUE)
```

**Cycle 2 Modeling Statistics**
```{r Cycle 2 Table, results='asis', message=FALSE, echo=FALSE, cache=TRUE}
stargazer(model_A2, model_B2, model_C2, model_D2, model_E2, model_F2, model_G2, model_H2, model_I2, model_J2, type = "html", notes.append = FALSE, notes.label = "Symbols", notes = c("<sup>&#42;</sup>p<0.1; <sup>&#42;&#42;</sup>p<0.05; <sup>&#42;&#42;&#42;</sup>p<0.01"), keep.stat = "adj.rsq", column.labels = c("A2", "B2","C2", "D2","E2", "F2","G2", "H2","I2", "J2"), multicolumn = TRUE, ci = TRUE)
```

**Cycle 3 Modeling Statistics**
```{r Cycle 3 Table, results='asis', message=FALSE, echo=FALSE, cache=TRUE}
stargazer(model_A3, model_B3, model_C3, model_D3, model_E3, model_F3, model_G3, model_H3, model_I3, model_J3, type = "html", notes.append = FALSE, notes.label = "Symbols", notes = c("<sup>&#42;</sup>p<0.1; <sup>&#42;&#42;</sup>p<0.05; <sup>&#42;&#42;&#42;</sup>p<0.01"), keep.stat = "adj.rsq", column.labels = c("A3", "B3","C3", "D3","E3", "F3","G3", "H3","I3", "J3"), multicolumn = TRUE, ci = TRUE)
```

**Cycle 4 Modeling Statistics**
```{r Cycle 4 Table, results='asis', message=FALSE, echo=FALSE, cache=TRUE}
stargazer(model_A4, model_B4, model_C4, model_D4, model_E4, model_F4, model_G4, model_H4, model_I4, model_J4, type = "html", notes.append = FALSE, notes.label = "Symbols", notes = c("<sup>&#42;</sup>p<0.1; <sup>&#42;&#42;</sup>p<0.05; <sup>&#42;&#42;&#42;</sup>p<0.01"), keep.stat = "adj.rsq", column.labels = c("A4","B4","C4","D4","E4","F4","G4","H4","I4","J4"), multicolumn = TRUE, ci = TRUE)
```

**Cycle 5 Modeling Statistics**
```{r Cycle 5 Table, results='asis', message=FALSE, echo=FALSE, cache=TRUE}
stargazer(model_A5, model_B5, model_C5, model_D5, model_E5, model_F5, model_G5, model_H5, model_I5, model_J5, type = "html", notes.append = FALSE, notes.label = "Symbols", notes = c("<sup>&#42;</sup>p<0.1; <sup>&#42;&#42;</sup>p<0.05; <sup>&#42;&#42;&#42;</sup>p<0.01"), keep.stat = "adj.rsq", column.labels = c("A5","B5","C5","D5","E5","F5","G5","H5","I5","J5"), multicolumn = TRUE, ci = TRUE)
```



